EDLD 651 Final Project Presentation

### 2020-11-30 chaloupka_sameshima_wallner_final_project.Rmd
Updated with Ben's text

new_data_for_later <- fractal_data %>% 
  group_by(direction) %>% 
  summarise(mean_dwell_time = round(mean(dwell_time), 3),
            sd_dwell_time = round(sd(dwell_time), 3))

fractal_data %>% 
  ggplot(aes(x = direction, y = dwell_time, fill = direction)) +
  geom_col(data = new_data_for_later, aes(y = mean_dwell_time)) +
  labs(x = "Direction", y = "Dwell Time (s)", title = "Dwell Times by Condition") +
  theme(legend.position = "none") +
  scale_fill_viridis_d()

>>>>

new_data_for_later <- fractal_data %>% 
  group_by(direction) %>% 
  summarise(mean_dwell_time = round(mean(dwell_time), 3),
            sd_dwell_time = round(sd(dwell_time), 3),
            mean_se_dwell_time = round(plotrix::std.error(dwell_time), 3))

ymin = new_data_for_later$mean_dwell_time - new_data_for_later$mean_se_dwell_time
ymax =new_data_for_later$mean_dwell_time + new_data_for_later$mean_se_dwell_time

new_data_for_later %>% 
  ggplot(aes(x = direction, y = mean_dwell_time, fill = direction)) +
  geom_col() +
  labs(x = "Direction", y = "Dwell Time (s)", title = "Dwell Times by Condition") +
  theme(legend.position = "none") +
  geom_errorbar(aes(ymin = ymin, ymax = ymax, width = .5)) +
  scale_fill_viridis_d()

### 2020-11-30 presentation.Rmd
Updated with Ben's text

# Dwelling on Complexity with Dynamic Fractals

*How much time will participants spend looking at dynamic fractals as they increase or decrease in complexity?*

@@

## Challenges faced along the way

this text will appear on the slide

## Victories and things to celebrate

<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/Fractal Dwell Time Schematic.jpg" height="360" width="480">

## Challenges you are still facing

## Next R hurdle to tackle

@@

## 
<!-- Ben -->

## 
<!-- Tess -->
<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/ovr_dwell_time2.png" height = "300" width = "400">

>>>>

## Dwelling on Complexity with Dynamic Fractals

How much time will participants spend looking at dynamic fractals as they increase or decrease in complexity?

@@

## Challenges faced along the way
- Working with Git
  - Figuring out best practices for collaboration
- Working with GGPlot
  - Getting figures to display the right data
- Not getting distracted by all the pretty fractals

## Victories and things to celebrate
- We made our presentation in R
- We made a lot of sweet plots
- We worked well as a team
- I came away from this project knowing more about R than I did before

## Challenges you are still facing
- Touching up some plots
- Getting more efficient using Git

## Next R hurdle to tackle
- Use functions we learned in class on my own data
- Get better at commenting my code

@@

## 
<!-- Ben -->
<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/group1.png" height = "600" width = "800">

##
<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/group2.png" height = "600" width = "800">

## 
<!-- Tess -->
<img src="/Users/bchaloup/Documents/Fall 2020/EDLD651/final_project/presentation_images/ovr_dwell_time2.png" height = "600" width = "800">
